### 2015-04-23 paper.tex
Discuss data processing

>>>>

\subsection*{Data Processing}

For each tow, a relevant quasi-steady duration is selected, and then truncated
to include a whole number of blade passages. Over this duration relevant
statistics are calculated.

To calculate turbine RPM from shaft angle, the encoder signal is differentiated
using a second order central difference scheme, after which a relatively
small-windowed moving average smoothing filter is applied to match the noise
level present in the redundant turbine RPM measurement from the motion
controller. A similar approach is used for calculating tow carriage speed
$U_\infty$ from carriage position measurements. Power and drag coefficients are
calculated as instantaneous quantities from the carriage speed as

\begin{equation}
C_P = \frac{T \omega}{\frac{1}{2} \rho A U_\infty^3}
\end{equation}
and
\begin{equation}
C_D = \frac{F_\mathrm{drag}}{\frac{1}{2} \rho A U_\infty^2},
\end{equation}
where $\rho$ is the fluid density (1000 kg/m\textsuperscript{3}) and $A$ is
the turbine frontal area $DH$.

All data processing and plotting code, along with the reduced dataset are
available from \cite{Bachant2015-RM2-data}. Note that this code will
automatically download raw data as necessary so users can perform a full
reanalysis of the measurements presented here.
